Vision and Cognitive Systems Final Project

### 2020-06-30 Paper_Presentation/paper/paper.tex
paper updates 2

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../Orb_matches/match3.png}}
\caption{Orb matches}
\label{fig}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../detection_and_rectification/top_association_vid05.png}}
\caption{Painting detection and rectification}
\label{fig}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../people_detection/paint_and_person.png}}
\caption{People detection}
\label{fig}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../people_detection/people_error.png}}
\caption{People detection error}
\label{fig}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../people_detection/people_error_fixed.png}}
\caption{People detection error fixed}
\label{fig}
\end{figure}

@@

\section{Painting Replacement in the 3D Model}
the pipeline followed to accomplish this task is similar to the one explained before with a little difference. we start directly with the hsv version of the image taken as input (a screenshot from the 3d model); then we apply Otsu threshold, followed by noise removal thanks to opening or closing process, keeping the one that maximizes the number of contours found. At this point we loop over each contour and find an approximation of itself with approxPolyDP; if the approximation has a shape described by 4 vertices, we estimate keypoints with orb and fetch the corresponding image from the database. Once this is done, if the image fetched is judged as a good match, we align that image with respect to the screenshot’s image plane and superimpose the result on the input image.
what is worth to mention is that the alignment function that we use in this process is the same of the main pipeline of painting rectification. this function in fact takes as input two images and project the first one on the plane of the second. if the second image is a painting fetched from the database, it means that the first image is rectified; if instead the second image is a painting coming from a frame/screenshot, it means that we want to distort an image in order to match the perspective of that painting.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../Labeling_precision_metrics/Precision_Labeling.png}}
\caption{labeling.}
\label{fig}
\end{figure}

@@

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

>>>>

\section{Related Works}
To remove camera noise but maintains the contours a  Bilateral filter is used.
C. Tomasi and R. Manduchi, "Bilateral filtering for gray and color images," Sixth International Conference on Computer Vision (IEEE Cat. No.98CH36271), Bombay, India, 1998, pp. 839-846, doi: 10.1109/ICCV.1998.710815.

OTSU is an automatic thresholding method widely used when the numbers of pixels in each class are close to each other.
J. Zhang and J. Hu, "Image Segmentation Based on 2D Otsu Method with Histogram Analysis," 2008 International Conference on Computer Science and Software Engineering, Hubei, 2008, pp. 105-108, doi: 10.1109/CSSE.2008.206.

Opencv Find Counturs function is been used to find counturs in a previouslly modified frame in order to detect painting
Suzuki, S., and Be, K. (1985). Topological structural analysis of digitized binary images by border following. Computer Vision, Graphics, and Image Processing 30, 32–46. doi:10.1016/0734-189X(85)90016-7.

The functions approxPolyDP approximate a curve or a polygon with another curve/polygon with less vertices so that the distance between them is less or equal to the specified precision. It uses the Douglas-Peucker algorithm

ORB E. Rublee, V. Rabaud, K. Konolige and G. Bradski, "ORB: An efficient alternative to SIFT or SURF," 2011 International Conference on Computer Vision, Barcelona, 2011, pp. 2564-2571, doi: 10.1109/ICCV.2011.6126544.

YoloV3 is a famous neural network for fast object detection, will be used in this paper for people detection
Redmon, Joseph and Ali Farhadi. “YOLOv3: An Incremental Improvement.” ArXiv abs/1804.02767 (2018): n. pag.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../Orb_matches/match3.png}}
\caption{Orb matches}
\label{fig_Orb_matches}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../detection_and_rectification/top_association_vid05.png}}
\caption{Painting detection and rectification}
\label{fig_Painting_detection_and_rectification}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../people_detection/paint_and_person.png}}
\caption{People detection}
\label{fig_People_detection}
\end{figure}

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../people_detection/people_error.png}}
\caption{People detection error}
\label{fig_People_detection_error}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../people_detection/people_error_fixed.png}}
\caption{People detection error fixed}
\label{fig_People_detection_error_fixed}
\end{figure}

@@

\section{Painting Replacement in the 3D Model}
The pipeline followed to accomplish this task is similar to the one explained before with a little difference. we start directly with the hsv version of the image taken as input (a screenshot from the 3d model); then we apply Otsu threshold, followed by noise removal thanks to opening or closing process, keeping the one that maximizes the number of contours found. At this point we loop over each contour and find an approximation of itself with approxPolyDP; if the approximation has a shape described by 4 vertices, we estimate keypoints with orb and fetch the corresponding image from the database. Once this is done, if the image fetched is judged as a good match, we align that image with respect to the screenshot’s image plane and superimpose the result on the input image.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../screenshots_3d_model/screenshot_01.jpg}}
\caption{3dmodel}
\label{fig_3d_model}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../screenshots_3d_model/screenshot_03.png}}
\caption{3d model 2}
\label{fig_3d_model_2}
\end{figure}

What is worth to mention is that the alignment function that we use in this process is the same of the main pipeline of painting rectification. this function in fact takes as input two images and project the first one on the plane of the second. if the second image is a painting fetched from the database, it means that the first image is rectified; if instead the second image is a painting coming from a frame/screenshot, it means that we want to distort an image in order to match the perspective of that painting.

@@

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.8\columnwidth]{../Labeling_precision_metrics/Precision_Labeling.png}}
\caption{labeling}
\label{fig_labeling}
\end{figure}

@@

\section*{Discussions}
L’approccio seguito si fonda sull’assunzione che nel video in questione sia presente una buona differenza cromatica tra background e paintings. nel caso questa condizione non sia verificata, come nel caso di una inquadratura più ampia comprendente non solo quadri e parete ma anche corridoio ad esempio, otsu non riesce a dividere correttamente quadri da background e le performance della detection calano.
cronologia degli approcci testati
inizialmente si è pensato di utilizzare Canny, preceduto da una rimozione iniziale di rumore prodotta dal bilateral filter, per trovare i bordi su cui applicare findContours. i risultati non erano del tutto soddisfacenti in quanto spesso i contorni prodotti da canny non individuavano con precisione il quadro. abbiamo quindi optato per una soluzione basata sul thresholding dell’immagine rgb, che come già spiegato in precedenza è seguita da un raffinamento effettuato a livello hsv. Si è anche testato un metodo basata solo su immagini hsv, che ha rivelato essere molto performante in certe situazioni (in ogni frame vi è una chiara distinzione tra quadro e background) ma meno stabile rispetto al metodo precedentemente esposto.

\section*{References}
Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
